Target Markdown

### 2022-09-12 _targets.Rmd
changed pipeline - mapping now within all_authors function

     tar_target(matching, match(db_path, ids),
                format = "qs"),
     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
     tar_target(ids_full_vector,
               make_ids_full_vector(matching)),
     tar_target(all_pubs,
           get_all_pubs(db_path, matching, ids_complete), 
              format = "qs"),
    tar_target(one_author,
           read_one_author(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector), 
              format = "qs", pattern = map(head(ids_full_vector,3)), iteration = "list")

>>>>

     tar_target(matching, match(db_path, ids),
                format = "qs"),
     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
     tar_target(ids_full_vector,
               make_ids_full_vector(matching)),
     tar_target(all_pubs,
           get_all_pubs(db_path, matching, ids_complete), 
              format = "qs"),
    # tar_target(one_author,
           # read_one_author(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector), 
           #    format = "qs", pattern = map(head(ids_full_vector,3)), iteration = "list"),
    tar_target(all_authors,
           read_all_authors(db_path, ids_complete_vector, ids_complete, matching, ids_full_vector), 
              format = "qs")
